Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
improved

\subsection{Cluster}
Here we present real patterns that are closer to the code presented in ...
than any other code. The goal is to feel how much variance is present in
a cluster. See Figure \ref{fig:cluster}.

>>>>

\subsection{Cluster}
Once we understand the kind of codebook we create, we naturally want
to visualize the clusters, i.e. the pattersn from actual song that
surround a given centroid. Unsurprisingly, real patterns tend to be
noisier than codes. However, centroids seem to capture important aspects
of the patterns. We could compare the centroids with the result of
a lowpass filtering.

See Figure \ref{fig:cluster}.
